The Calibration Reference Data System

### 2016-03-16 docs/paper/response.txt

A section at the end has been added that briefly describes what Spitzer, 
Chandra and Gemini use and notes some of the restrictions entailed in their
approaches (Chandra's is most similar in approach but simpler).

As far as the implications regarding databases go, we have not expanded on that.
This is mainly because some issues are arguably self evident (distributing
software that requires databases certainly does impose a significantly larger 
burden on those installing and maintaining such a system; we doubt that is 
controversial).

We also think it is nearly self evident that SQL does not always represent 
rules in a clear or easy to understand way (and many astronomers, the ones 
that ultimately must provide those rules, are not experts in SQL, particularly
complex SQL). We aren't saying it is impossible to use only SQL, just not 
ideal. Indeed, Gemini's experience found it to be too constricting (as we did).
Chandra doesn't use it at all, and it appears Spitzer's needs are not as complex.
This is probably aided by the fact that they generally process the data in 
large runs, i.e,. their updates are relatively infrequent as we understand 
it.  Besides, they sometimes have special processing after the query (e.g., 
interpolation between two reference files), so it isn't a pure database
solution either. Accomodating new needs requires new software changes.
To be fair, so does ours if a new kind of rule is required, but that
is much less likely, and much more likely to be in adding a new module
rather than changing existing code.

It really isn't our intent to argue that databases are not appropriate; rather 
for the features we sought, that they did not appear to be the simplest
solution. In things like this, proving it beyond any question is not
something that projects have the resources to do. Indeed, practically 
speaking, there never is proof, only indications by the absense of
solutions using them. The only proof possible is proving that they
are suitable by implementing a system that has the features we sought
using a database. Doing that really is for someone else to do. We can 
only note that we haven't found one in existance yet.

As to the focus on STScI needs. We don't agree that only one page
is devoted to generic needs. We would argue that the great majority
of the discussion is directed to generic capabilities, with occasional
references to how they relate to JWST or HST. Yes, the examples are for
STScI systems, but it would be odd for us to use examples for other
observatories for which we are not qualified to provide. We don't 
believe that these examples in any way limit the generic aspects of
the system.

But even if it were the case it wasn't sufficiently generic enough, it's
a question of having enough resources 
to develop a system with a very broad reach and goals initially (well, perhaps,
many very ambitious projects die for being too ambitious!). But with the
reality of funding oversight it's very difficult to do that. NASA gets 
quite nervous when they see work being done that isn't specifically done
for their mission. We do what we can to keep the project more broadly 
useful within these constraints, and we think we have done as much as
possibly can be expected along those lines. That's even true when writing
papers (i.e., can we justify spending much time doing a thorough survey 
of all systems out there?).

### 2016-03-16 docs/paper/crds.tex
last version, I hope
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2250 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

@@

We describe a software architecture and implementation for using rules to
determine which calibration files are appropriate for calibrating a
given observation. This new system, the Calibration Reference Data System
(CRDS), replaces what had been previously used for
the Hubble Space Telescope (HST) calibration pipelines, 
the Calibration Database System (CDBS). 
CRDS will be used for the James Webb Space
Telescope (JWST) calibration pipelines, and is currently
being used for HST calibration pipelines. CRDS can be
easily generalized for use in similar applications that need a rules-based
system for selecting the appropriate item for a given dataset; we give some
examples of such generalizations that will likely be used for JWST. The core
functionality of the Calibration Reference Data System is available under an
Open Source license. CRDS is briefly constrasted with a selected 
sampling of other similar systems used at other observatories.
\end{abstract}

@@

\newpage

@@

The approach Chandra uses is based on the CALDB approach developed by 
HEASARC and used by most high-engergy missions 
(\citealt{2006SPIE.6270E..1XG}). Despite
the name, no database is involved. In fact, the approach is a simpler 
version of what is described in this paper. Essentially, the rules for 
selecting files is kept in index files that list all of the available 
calibration reference files and the situations they should be used for. 
It shares some of the advantages of our approach such as being able to 
recreate past recommendations and being able to distribute the software, 
though it isn’t as simple to set up.

@@

Spitzer uses perhaps the purest database approach we are aware of, and 
has been described in \citealt{2005ASPC..347..594L}. 
While it does permit an easy undo of updates, 
it is difficult to recreate past recommendations, and is not easy to 
distribute and run elsewhere (besides, the code and the associate 
database does not appear to be available to do so).
The rules for selection of calibration reference 
files are basically expressed as as SQL queries to the database.
Special post query processing is sometimes done, such as generating
a time-interpolated reference from two bracketing files.

@@

As such, it isn’t easy to support multiple 
versions of the rules (that requires multiple servers), nor can the 
system be easily distributed or customized without a lot of expertise 
(but it can be used remotely through the web, and there is consideration 
being given to mechanisms to allow local customization to the web results). 
Reversion may be possible by using version control to reinstate the 
appropriate Python modules, but has never been used in practice; 
for the results to be replicated accurately requires that none of the
information in the database for files present at that time of the previous
results has been changed since that time.

>>>>

\hyphenation{bestref}

@@

We describe a software architecture and implementation for using rules to
determine which calibration files are appropriate for calibrating a
given observation. This new system, the Calibration Reference Data System
(CRDS), replaces what had been previously used for
the Hubble Space Telescope (HST) calibration pipelines, 
the Calibration Database System (CDBS). 
CRDS will be used for the James Webb Space
Telescope (JWST) calibration pipelines, and is currently
being used for HST calibration pipelines. CRDS can be
easily generalized for use in similar applications that need a rules-based
system for selecting the appropriate item for a given dataset; we give some
examples of such generalizations that will likely be used for JWST. The core
functionality of the Calibration Reference Data System is available under an
Open Source license. CRDS is briefly constrasted with a 
sampling of other similar systems used at other observatories.
\end{abstract}

@@

@@

The approach Chandra uses is based on the CALDB approach developed by 
HEASARC and used by most high-engergy missions 
(\citealt{2006SPIE.6270E..1XG}). Despite
the name, no database is involved. In fact, the approach is a simpler 
version of what is described in this paper. Essentially, the rules for 
selecting files is kept in index files that list all of the available 
calibration reference files and the situations they should be used for. 
It shares some of the advantages of our approach such as being able to 
recreate past recommendations and being able to distribute the software, 
though it is not as simple to set up.

@@

Spitzer uses perhaps the purest database approach we are aware of, and 
has been described in \citealt{2005ASPC..347..594L}. 
While it does permit an easy undo of updates, 
it is difficult to recreate past recommendations, and is not easy to 
distribute and run elsewhere (besides, the code and the associate 
database does not appear to be available to do so).
The rules for selection of calibration reference 
files are basically expressed as as SQL queries to the database.
Special post-query processing is sometimes done, such as generating
a time-interpolated reference from two bracketing files.

@@

As such, it is not easy to support multiple 
versions of the rules (that requires multiple servers), nor can the 
system be easily distributed or customized without a lot of expertise 
(but it can be used remotely through the web, and there is consideration 
being given to mechanisms to allow local customization to the web results). 
Reversion may be possible by using version control to reinstate the 
appropriate Python modules, but has never been used in practice; 
for the results to be replicated accurately requires that none of the
information in the database for files present at that time of the previous
results has been changed since that time.
